
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}



% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{description}}
\newcommand{\resumeSubHeadingListEnd}{\end{description}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%------------- Resume starts here -----------------------


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://amirraminfar.me/}{\Large Amir Raminfar}} & Email : \href{mailto:findamir@gmail.com}{findamir@gmail.com}\\
  \href{https://amirraminfar.me/}{https://amirraminfar.me} & Mobile : +1-202-549-7332 \\
\end{tabular*}


% Experience
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Google}{Mountain View, CA}
      {Engineering Manager}{2019 - Present}
      \resumeItemListStart
        \item Engineering lead for Google’s internal CRM portfolio tools for enabling sellers to do quarterly quota setting, updating weekly forecasts and managing daily customer relationships.
        \item Responsible and accountable for prioritizing a multi-year set of OKRs with product, biz and UX with 16 engineers and three TLs.
        \item Provide technical leadership for team’s FE infrastructure team on best practices for a11y, developer happiness and engineering excellence, such as latency.
        \item Managed performance and promotion for 10 engineers with a 98\% people manager score.
      \resumeItemListEnd

    \resumeSubheading
      {Ujet.co}{San Francisco, CA}
      {Engineering Director}{2018 - 2019}
      \resumeItemListStart
        \item Moved monolithic Rails application to micro-services written in Go optimized for 3,750 qps deployed in AWS EKS.
        \item Leading a team of 15 engineers, three tech leads for the SRE, Server \& API design and ML efforts.
        \item Product owner for all of UJET’s security efforts. Architected and launched an authentication platform which integrated with OpenAuth, Auth0 and Okta using an internal JWT implementation for our SOA.
        \item Introduced Apache Kafka, Elasticsearch and Logstash to enable a real-time analytical reporting engine written in Go and deployed to production to power all of UJET’s customer facing dashboards.
      \resumeItemListEnd

    \pagebreak[3]

    \resumeSubheading
    {Capital One}{San Francisco, CA}
    {Engineering Director}{2017 - 2018}
    \resumeItemListStart
      \item Technology leader for the labs and innovation teams in SF. Managed a team of 20 engineers with two managers.
      \item Pitched and built a content management system to power all of Capital One’s promotion modules on mobile devices. Tracked user engagement over time for data analytics and customer retention in Apache Spark.
      \item Migrated all internal micro-services to Docker on AWS EKS with 99.9\% uptime built on Java, Go and Python.
      \item Product owner for all Capital One cryptocurrency products. Integrated our wallet app with Coinbase, Chain.io and other smart contract providers. Launched an internal blockchain platform which is still used across all business platform teams.
    \resumeItemListEnd

    \pagebreak[3]

    \resumeSubheading
    {Quid, Inc}{San Francisco, CA}
    {Engineering Director}{2016 - 2017}
    \resumeItemListStart
      \item Executed on the long-term vision for the web platform: decomposing our monolithic application to micro-services architecture and integrating with third-party services like Auth0, LaunchDarkley and BugSnag.
      \item Provided technical leadership for Docker migration with the SRE team and deployed to production in OpenShift.
      \item Improved the hiring process with the recruiting team by introducing a set of consistent new interview questions and pre-screening phone calls yielding in four hires in half the time.
    \resumeItemListEnd

    \pagebreak[3]

    \resumeSubheading
    {Opower (acquired by Oracle)}{San Francisco, CA}
    {Engineering Director}{2011 - 2016}
    \resumeItemListStart
      \item Engineering leader for the email, paper reports and all digital communications with six engineering managers as direct reports and 60 ICs.
      \item Delivered a four-year product roadmap for our outbound communication products which send paper and digital reports to 50+ million households per week.
      \item Responsible for the quarter deliverables consisting of ten consumer-facing products and four platform initiatives with technical roadmap migrating to Docker and deployment in AWS.
      \item Participated in design reviews and architectural decisions with the CTO and VP of engineering. Delivered improvements to internal communication platform resulting in 16x improvement in throughput.
      \item Actively hired and interviewed engineers, designers, and product managers. Improved the quality of our interview process by changing phone interview and technical questions. Hired over 15 senior engineers and managers since 2014.
      \item Planned and executed a process in which engineers self-selected into their scrum teams. Resulted in 90% overall happiness across all engineering teams.
    \resumeItemListEnd

  \resumeSubHeadingListEnd

  \pagebreak[3]
  % Education
  \section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {The George Washington University}{Washington, DC}
      {Master of Science in Computer Science}{2011}
    \resumeSubheading
      {The George Washington University}{Washington, DC}
      {Bachelor of Science in Computer Science}{2005}
  \resumeSubHeadingListEnd

  \pagebreak[3]
% Projects
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Dozzle for Docker}
      {Creator of open-source project to view container logs using Docker API written in Go with one million weekly downloads.}
    \resumeSubItem{Clashleaders.com}
      {Web app written in VueJs, Python DataFrames and Docker to track trends and leaderboards for the Clash of Clan game. Total of 5,000 monthly active users.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
